Supporting Information

### 2018-04-02 SupportingInformation.Rmd
multipanel (11 fig) plot for aphid and plankton added

<!--Shya, can you please add panels for corl, coru, Pl, Pu, D2l, D2u vs. distance, following the Spearman and Kendall
panels? I think it will be the first time anyone has shown these, so we should show the decline with distance
holds for these as well. That means you'll have 6 new panels, for a total of 11 panels. So it'll be a big figure, 
possibly taking up a whole page, or most of one. Similar changes, please,
to the analogous figs for the aphid ff and ceratium furca data.-->
\begin{figure}[!h]
\begin{center}
\textbf{\;\;\;\;\;\;\;\ (A) \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\ (B)} \\
\includegraphics[width=2in]{./Results/stat_results/stat_aphid_count/Sp_10_Spearman_vs_D.pdf}
\includegraphics[width=2in]{./Results/stat_results/stat_aphid_count/Sp_10_Kendall_vs_D.pdf}\\
\textbf{\;\;\;\;\;\;\;\ (C) \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\ (D)} \\
\includegraphics[width=2in]{./Results/stat_results/stat_aphid_count/Sp_10_Corl-Coru_vs_D.pdf}
\includegraphics[width=2in]{./Results/stat_results/stat_aphid_count/Sp_10_Pl-Pu_vs_D.pdf}\\
\textbf{\;\;\;\;\;\;\;\ (E)} \\
\includegraphics[width=2in]{./Results/stat_results/stat_aphid_count/Sp_10_D2u-D2l_vs_D.pdf}
\caption{Non-parametric tail statistics results for green spruce aphid abundance data plotted against geographical distance ($D$) between two sampling locations. (A) Spearman correlation vs. $D$; (B) Kendall correlation vs. $D$; (C) $\cor_l$ vs. $D$; (D) $\cor_u$ vs. $D$; (E) $\Ps_l$ vs. $D$; (F) $\Ps_u$ vs. $D$; (G) $\Dsq_u$ vs. $D$; 
(H) $\Dsq_l$ vs. $D$; 
(I) $\cor_l-\cor_u$ vs. $D$, (J) $\Ps_l-\Ps_u$ vs. $D$, (K) $\Dsq_u-\Dsq_l$ vs. $D$ plotted for all 
pairs of locations. \label{fig_aphid_count}}
\end{center}
\end{figure}

@@

<!--Shya, pls add 6 new panels as described in my comment near the analogous figure for aphid count-->
\begin{figure}[!h]
\begin{center}
\textbf{\;\;\;\;\;\;\;\ (A) \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\ (B)} \\
\includegraphics[width=2in]{./Results/stat_results/stat_aphid_ff/Sp_11_Spearman_vs_D.pdf}
\includegraphics[width=2in]{./Results/stat_results/stat_aphid_ff/Sp_11_Kendall_vs_D.pdf}\\
\textbf{\;\;\;\;\;\;\;\ (C) \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\ (D)} \\
\includegraphics[width=2in]{./Results/stat_results/stat_aphid_ff/Sp_11_Corl-Coru_vs_D.pdf}
\includegraphics[width=2in]{./Results/stat_results/stat_aphid_ff/Sp_11_Pl-Pu_vs_D.pdf}\\
\textbf{\;\;\;\;\;\;\;\ (E)} \\
\includegraphics[width=2in]{./Results/stat_results/stat_aphid_ff/Sp_11_D2u-D2l_vs_D.pdf}
\caption{Non-parametric tail statistics results for leaf-curling plum aphid's first flight date data plotted against geographical distance $(D)$ between two sampling locations. (A) Spearman correlation vs. $D$, (B) Kendall correlation vs. $D$, (C) $\cor_l$ vs. $D$, (D) $\cor_u$ vs. $D$; (E) $\Ps_l$ vs. $D$; (F) $\Ps_u$ vs. $D$; (G) $\Dsq_u$ vs. $D$; (H) $\Dsq_l$ vs. $D$; (I) $\cor_l-\cor_u$ vs. $D$; (J) $\Ps_l-\Ps_u$ vs. $D$; (K) $\Dsq_u-\Dsq_l$ vs. $D$ plotted for all pairs of locations. \label{fig_aphid_ff}}
\end{center}
\end{figure}

@@

![copula plot for Plankton_north_sea\label{fig_pns_allcop}](./Results/stat_results/stat_plankton_north_sea/Sp_16_AllCops.pdf)

![Plot for Plankton_north_sea : Spearman vs. Distance\label{fig_pns_spear}](./Results/stat_results/stat_plankton_north_sea/Sp_16_Spearman_vs_D.pdf){ width=50%, height=50% }

![Plot for Plankton_north_sea : Kendall vs. Distance\label{fig_pns_kend}](./Results/stat_results/stat_plankton_north_sea/Sp_16_Kendall_vs_D.pdf){ width=50%, height=50% }

![$cor_l$-$cor_u$ vs. Distance plot for Plankton_north_sea showing lower tail dependence\label{fig_pns_Corl-Coru}](./Results/stat_results/stat_plankton_north_sea/Sp_16_Corl-Coru_vs_D.pdf){ width=50%, height=50% }

![$P_l$-$P_u$ vs. Distance plot for Plankton_north_sea showing lower tail dependence\label{fig_pns_Pl-Pu}](./Results/stat_results/stat_plankton_north_sea/Sp_16_Pl-Pu_vs_D.pdf){ width=50%, height=50% }

![$D^2_u$-$D^2_l$ vs. Distance plot for Plankton_north_sea showing lower tail dependence\label{fig_pns_D2u-D2l}](./Results/stat_results/stat_plankton_north_sea/Sp_16_D2u-D2l_vs_D.pdf){ width=50%, height=50% }

>>>>

<!--Shya, can you please add panels for corl, coru, Pl, Pu, D2l, D2u vs. distance, following the Spearman and Kendall
panels? I think it will be the first time anyone has shown these, so we should show the decline with distance
holds for these as well. That means you'll have 6 new panels, for a total of 11 panels. So it'll be a big figure, 
possibly taking up a whole page, or most of one. Similar changes, please,
to the analogous figs for the aphid ff and ceratium furca data.-->
\begin{figure}[!h]
\textbf{ \hspace{2.6 cm} (A) \hspace{3.6 cm} (B) \hspace{3.8 cm} (C) \hspace{3.8 cm} (D)} \\
\begin{center}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_count/Sp_10_Spearman_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_count/Sp_10_Kendall_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_count/Sp_10_Corl_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_count/Sp_10_Coru_vs_D.pdf}\\
\end{center}
\textbf{ \hspace{2.6 cm} (E) \hspace{3.6 cm} (F) \hspace{3.8 cm} (G) \hspace{3.8 cm} (H)} \\
\begin{center}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_count/Sp_10_Pl_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_count/Sp_10_Pu_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_count/Sp_10_D2u_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_count/Sp_10_D2l_vs_D.pdf}\\
\end{center}
\textbf{ \hspace{4.8 cm} (I) \hspace{3.8 cm} (J) \hspace{4 cm} (K) } \\
\begin{center}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_count/Sp_10_Corl-Coru_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_count/Sp_10_Pl-Pu_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_count/Sp_10_D2u-D2l_vs_D.pdf}
\caption{Non-parametric tail statistics results for green spruce aphid abundance data plotted against geographical distance ($D$) between two sampling locations. (A) Spearman correlation vs. $D$; (B) Kendall correlation vs. $D$; (C) $\cor_l$ vs. $D$; (D) $\cor_u$ vs. $D$; (E) $\Ps_l$ vs. $D$; (F) $\Ps_u$ vs. $D$; (G) $\Dsq_u$ vs. $D$; 
(H) $\Dsq_l$ vs. $D$; 
(I) $\cor_l-\cor_u$ vs. $D$, (J) $\Ps_l-\Ps_u$ vs. $D$, (K) $\Dsq_u-\Dsq_l$ vs. $D$ plotted for all 
pairs of locations. \label{fig_aphid_count}}
\end{center}
\end{figure}

@@

<!--Shya, pls add 6 new panels as described in my comment near the analogous figure for aphid count-->
\begin{figure}[!h]
\textbf{ \hspace{2.6 cm} (A) \hspace{3.6 cm} (B) \hspace{3.8 cm} (C) \hspace{3.8 cm} (D)} \\
\begin{center}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_ff/Sp_11_Spearman_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_ff/Sp_11_Kendall_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_ff/Sp_11_Corl_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_ff/Sp_11_Coru_vs_D.pdf}\\
\end{center}
\textbf{ \hspace{2.6 cm} (E) \hspace{3.6 cm} (F) \hspace{3.8 cm} (G) \hspace{3.8 cm} (H)} \\
\begin{center}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_ff/Sp_11_Pl_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_ff/Sp_11_Pu_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_ff/Sp_11_D2u_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_ff/Sp_11_D2l_vs_D.pdf}\\
\end{center}
\textbf{ \hspace{4.8 cm} (I) \hspace{3.8 cm} (J) \hspace{4 cm} (K) } \\
\begin{center}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_ff/Sp_11_Corl-Coru_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_ff/Sp_11_Pl-Pu_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_ff/Sp_11_D2u-D2l_vs_D.pdf}
\caption{Non-parametric tail statistics results for leaf-curling plum aphid's first flight date data plotted against geographical distance $(D)$ between two sampling locations. (A) Spearman correlation vs. $D$, (B) Kendall correlation vs. $D$, (C) $\cor_l$ vs. $D$, (D) $\cor_u$ vs. $D$; (E) $\Ps_l$ vs. $D$; (F) $\Ps_u$ vs. $D$; (G) $\Dsq_u$ vs. $D$; (H) $\Dsq_l$ vs. $D$; (I) $\cor_l-\cor_u$ vs. $D$; (J) $\Ps_l-\Ps_u$ vs. $D$; (K) $\Dsq_u-\Dsq_l$ vs. $D$ plotted for all pairs of locations. \label{fig_aphid_ff}}
\end{center}
\end{figure}

@@

\begin{figure}[!h]
\textbf{ \hspace{2.6 cm} (A) \hspace{3.6 cm} (B) \hspace{3.8 cm} (C) \hspace{3.8 cm} (D)} \\
\begin{center}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Spearman_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Kendall_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Corl_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Coru_vs_D.pdf}\\
\end{center}
\textbf{ \hspace{2.6 cm} (E) \hspace{3.6 cm} (F) \hspace{3.8 cm} (G) \hspace{3.8 cm} (H)} \\
\begin{center}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Pl_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Pu_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_D2u_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_D2l_vs_D.pdf}\\
\end{center}
\textbf{ \hspace{4.8 cm} (I) \hspace{3.8 cm} (J) \hspace{4 cm} (K) } \\
\begin{center}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Corl-Coru_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Pl-Pu_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_D2u-D2l_vs_D.pdf}
\caption{Non-parametric tail statistics results for Ceratium furca abundance data plotted against geographical distance $(D)$ between two sampling locations. (A) Spearman correlation vs. $D$, (B) Kendall correlation vs. $D$, (C) $\cor_l$ vs. $D$, (D) $\cor_u$ vs. $D$; (E) $\Ps_l$ vs. $D$; (F) $\Ps_u$ vs. $D$; (G) $\Dsq_u$ vs. $D$; (H) $\Dsq_l$ vs. $D$; (I) $\cor_l-\cor_u$ vs. $D$; (J) $\Ps_l-\Ps_u$ vs. $D$; (K) $\Dsq_u-\Dsq_l$ vs. $D$ plotted for all pairs of locations. \label{fig_pns}}
\end{center}
\end{figure}
